Supplemental Materials

### 2021-07-20 paper/paper.Rmd
minor fix
figure fixes

```{r load-required-data, include=FALSE}

```

@@

As in Study 2, we used our model to predict how the 13 other beliefs in the intuitive theory should be expected to change given the average magnitude of the change observed in participants’ vaccine toxicity beliefs following the intervention. As shown in Figure 5, the model’s predictions are significantly related to the observed changes, but the correlations are relatively weaker R = .XX than those observed in our other studies.

@@

We contacted XXX of the 1130 participants who completed Study 1 and invited them to participate in Study 4, in which they completed the same 14 belief scales and answered questions about their exposure to media coverage of the measles outbreaks. Of these, 555 participants returned and XXX successfully completed the study including passing attention checks. These participants completed all 14 belief scales and also indicated whether they had seen or heard anything about measles in the news recently.

@@

Mirroring our analyses of interventions, we regressed responses to the *vaccine intentions* scale items on predictors for phase (X 2017 vs. May 2019, dummy-coded), news exposure (dummy-coded with non-exposure as the baseline), and an interaction between phase and news exposure onto participants’ scores, using a Bayesian mixed-effects ordinal regression including random intercepts by subject and item. To assess the effects of recent news exposure on vaccine intentions, we examined the interaction between phase and news exposure. Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months ago (stats); see Figure 6, panel A.

>>>>

```{r load-required-data, include=FALSE}
results <- readRDS("../local/paper-results.rds") 
```

@@

As in Study 2, we used our model to predict how the 13 other beliefs in the intuitive theory should be expected to change given the average magnitude of the change observed in participants’ vaccine toxicity beliefs following the intervention. As shown in Figure 5, the model’s predictions are significantly related to the observed changes, but the correlations are relatively weaker (r = .XX) than those observed in our other studies.

@@

We contacted as many of the 1130 participants who completed Study 1 as we could and invited them to participate in Study 4, in which they completed the same 14 belief scales and answered questions about their exposure to media coverage of the measles outbreaks. A total of 555 participants returned and XXX successfully completed the study including passing attention checks. These participants completed all 14 belief scales and also indicated whether they had seen or heard anything about measles in the news recently.

@@

Mirroring our analyses of interventions, we regressed responses to the *vaccine intentions* scale items on predictors for phase (September 2017 vs. May 2019, dummy-coded), news exposure (dummy-coded with non-exposure as the baseline), and an interaction between phase and news exposure onto participants’ scores, using a Bayesian mixed-effects ordinal regression including random intercepts by subject and item. To assess the effects of recent news exposure on vaccine intentions, we examined the interaction between phase and news exposure. Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months ago (stats); see Figure 6, panel A.

### 2021-07-20 supplement/supplement-main.Rmd
figure fixes

z2 <- custom_plot.HydeNetwork(h2)

@@

# z$nodes_df
z2$nodes_df <- z2$nodes_df %>% mutate(label = recode_nodes(label))
z2$nodes_df$fontname <- "Helvetica"
z2$nodes_df$shape <- "ellipse"
z2$nodes_df$fillcolor <- ifelse(z2$nodes_df$label=="Vaccination\nIntentions", 
                                "#fffaba","white")
z2$nodes_df$fillalpha <- 0.1
z2$nodes_df$fixedsize <- FALSE
z2$edges_df$penwidth <- abs(edge_df_mod$strength)*2
z2$edges_df$penwidth <- 1.5
# z$edges_df$label <- round(edge_df_mod$value,2)
# z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
z2$edges_df$color <- map_to_brewer(edge_df_mod$strength, bins=9, option="RdPu")
# z2$edges_df$color <- map_to_viridis(edge_df_mod$strength, option="magma")
# 
# render_graph(z2)

@@

# z$nodes_df
z$nodes_df <- z$nodes_df %>% mutate(label = recode_nodes(label))
z$nodes_df$fontname <- "Helvetica"
z$nodes_df$shape <- "ellipse"
z$nodes_df$fillcolor <- ifelse(z$nodes_df$label=="Vaccination\nIntentions", "#fffaba","white")
z$nodes_df$fixedsize <- FALSE
z$edges_df$penwidth <- abs(edge_df_mod$value)*2
z$edges_df$penwidth <- 1.5
# z$edges_df$label <- round(edge_df_mod$value,2)
# z$edges_df$label <- edge_df_mod$label
# z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
z$edges_df$color <- map_to_brewer(edge_df_mod$value, bins=11, option="RdBu")

@@

s2_diff_plot <- s2_scored %>% 
  spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>% 
  # group_by(scale) %>% 
  # mutate(post = post/sd(post), pre = pre/sd(pre)) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = recode_factor(condition, 
                              "noInterv" = "Control",
                              .default = "Disease Risk")) %>% 
  group_by(condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ungroup() %>%
  left_join(s2_scale_order) %>%
  ggplot(aes(x = reorder(scale,order), y = M, 
             ymin = M-se*2, ymax=M+se*2, 
             color=condition, shape=condition)) +
  scale_x_discrete() +
  annotate("rect", 
           xmin = s2_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) - 0.25,
           xmax = s2_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) + 0.25,
           ymin = -Inf,
           ymax = Inf,
           fill = "#fffaba") +
  geom_pointrange(position=position_dodge(width=.25)) +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  scale_color_manual(values=c("#0067b1","#c50024")) +
  scale_shape_manual(values=c(16,17)) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.5,.9),
    legend.direction = "horizontal",
    legend.background = element_rect(fill = NA),
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", 
       color="Intervention", shape="Intervention")

@@

s3_diff_plot <- s3_scored %>% 
  # spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = recode_factor(condition, 
                              "noInterv" = "Control",
                              .default = "Vaccine Ingredients")) %>% 
  group_by(condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ungroup() %>%
  left_join(s3_scale_order) %>%
  ggplot(aes(x = reorder(scale,order), y = M, ymin = M-se*2, ymax=M+se*2, 
             color=condition, shape=condition)) +
  scale_x_discrete() +
  annotate("rect", 
           xmin = s3_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) - 0.25,
           xmax = s3_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) + 0.25,
           ymin = -Inf,
           ymax = Inf,
           fill = "#fffaba") +
  geom_pointrange(position=position_dodge(width=.25)) +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  scale_color_manual(values=c("#0067b1","#c50024")) +
  scale_shape_manual(values=c(16,17)) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.5,.1),
    legend.direction = "horizontal",
    legend.background = element_rect(fill = NA),
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", 
       color="Intervention", shape="Intervention")

@@

s3_diff_plot_bystudy <- s3_scored %>% 
  # spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = recode_factor(condition, 
                              "noInterv" = "Control",
                              .default = "Vaccine Ingredients")) %>% 
  left_join(s3_demo %>% distinct(workerId, study)) %>%
  mutate(study = recode_factor(study, "A" = "Expt. 3A", "B" = "Expt. 3B")) %>%
  group_by(study, condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ungroup() %>%
  left_join(s3_scale_order) %>%
  ggplot(aes(x = reorder(scale,order), y = M, ymin = M-se*2, ymax=M+se*2, 
             color = interaction(condition, study, sep = ": "), 
             shape = interaction(condition, study, sep = ": "))) +
  scale_x_discrete() +
  annotate("rect", 
           xmin = s3_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) - 0.35,
           xmax = s3_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) + 0.35,
           ymin = -Inf,
           ymax = Inf,
           fill = "#fffaba") +
  geom_pointrange(aes(group = interaction(condition, study)),
                  position=position_dodge(width=.4), fill = "white") +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  scale_color_manual(values=rep(c("#0067b1","#c50024"), 2)) +
  scale_shape_manual(values=c(16, 17, 21, 24)) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.5,.15),
    legend.direction = "horizontal",
    legend.background = element_rect(fill = NA),
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", 
       color="Intervention", shape="Intervention") +
  guides(shape = guide_legend(nrow = 2, byrow = T),
         color = guide_legend(nrow = 2, byrow = T))

@@

s4_diff_plot <- combined %>% 
  filter(returned==TRUE, !is.na(vacc_news)) %>% # somehow 5? participants slippd by without answering 
  mutate(posttest = rescale_beta(posttest, -3, 3), pretest = rescale_beta(pretest, -3, 3)) %>% 
  mutate(diff = posttest-pretest) %>%
  mutate(
    vacc_news = as.factor(vacc_news),
    scale = recode_nodes2(scale)
    ) %>%
  group_by(vacc_news,scale) %>%
  summarize(
    mean = mean(diff),
    se = sd(diff)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  mutate(vacc_news = factor(vacc_news, 
                            levels = c(0,1), 
                            labels=c("No","Yes"))) %>%
  # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
  left_join(s4_scale_order) %>%
  ggplot(aes(x=reorder(scale, order), 
             y = mean, ymin =ll95, ymax=ul95, 
             color=vacc_news, shape=vacc_news)) +
  scale_x_discrete() +
  annotate("rect", 
           xmin = s4_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) - 0.25,
           xmax = s4_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) + 0.25,
           ymin = -Inf,
           ymax = Inf,
           fill = "#fffaba") +
  geom_point(position=position_dodge(width=.25), size=2) +
  geom_errorbar(position=position_dodge(width=.25), width=0) +
  # geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
  geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
  scale_color_manual(values=c("#0067b1","#ff7f00")) +
  scale_shape_manual(values=c(16,17)) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.5,.9),
    legend.direction = "horizontal",
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", 
       color="News Exposure", shape="News Exposure")

@@

```{r measles-image, echo=F}
# display measles image here
```

@@

```{r mumps-image, echo=F}
# display mumps image here
```

@@

```{r rubellas-image, echo=F}
# display rubella image here
```

>>>>

z2 <- custom_plot.HydeNetwork(h2, attr_theme="tb")

@@

# z$nodes_df
z2$nodes_df <- z2$nodes_df %>% mutate(label = recode_nodes(label))
z2$nodes_df$fontname <- "Helvetica"
z2$nodes_df$shape <- "ellipse"
z2$nodes_df$fillcolor <- ifelse(z2$nodes_df$label=="Vaccination\nIntentions", 
                                "#dcdcdc","white")
z2$nodes_df$fillalpha <- 0.1
z2$nodes_df$fixedsize <- FALSE
z2$edges_df$penwidth <- abs(edge_df_mod$strength)*2
z2$edges_df$penwidth <- 1.5
# z$edges_df$label <- round(edge_df_mod$value,2)
# z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
z2$edges_df$color <- map_to_brewer(edge_df_mod$strength, bins=9, option="RdPu")
# z2$edges_df$color <- map_to_viridis(edge_df_mod$strength, option="magma")
# 
render_graph(z2)

@@

# z$nodes_df
z$nodes_df <- z$nodes_df %>% mutate(label = recode_nodes(label))
z$nodes_df$fontname <- "Helvetica"
z$nodes_df$shape <- "ellipse"
z$nodes_df$fillcolor <- ifelse(z$nodes_df$label=="Vaccination\nIntentions", "#dcdcdc","white")
z$nodes_df$fixedsize <- FALSE
z$edges_df$penwidth <- abs(edge_df_mod$value)*2
z$edges_df$penwidth <- 1.5
# z$edges_df$label <- round(edge_df_mod$value,2)
# z$edges_df$label <- edge_df_mod$label
# z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
z$edges_df$color <- map_to_brewer(edge_df_mod$value, bins=11, option="RdBu")

@@

s2_diff_plot <- s2_scored %>% 
  spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>% 
  # group_by(scale) %>% 
  # mutate(post = post/sd(post), pre = pre/sd(pre)) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = recode_factor(condition, 
                              "noInterv" = "Control",
                              .default = "Disease Risk")) %>% 
  group_by(condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ungroup() %>%
  left_join(s2_scale_order) %>%
  ggplot(aes(x = reorder(scale,order), y = M, 
             ymin = M-se*2, ymax=M+se*2, 
             color=condition, shape=condition)) +
  scale_x_discrete() +
  annotate("rect", 
           xmin = s2_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) - 0.25,
           xmax = s2_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) + 0.25,
           ymin = -Inf,
           ymax = Inf,
           fill = "#dcdcdc") +
  geom_pointrange(position=position_dodge(width=.25)) +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  scale_color_manual(values=c("#0067b1","#c50024")) +
  scale_shape_manual(values=c(17,16)) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.6,.9),
    legend.direction = "horizontal",
    legend.background = element_rect(fill = NA),
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", 
       color="Intervention", shape="Intervention")

@@

s3_diff_plot <- s3_scored %>% 
  # spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = recode_factor(condition, 
                              "noInterv" = "Control",
                              .default = "Vaccine Ingredients")) %>% 
  group_by(condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ungroup() %>%
  left_join(s3_scale_order) %>%
  ggplot(aes(x = reorder(scale,order), y = M, ymin = M-se*2, ymax=M+se*2, 
             color=condition, shape=condition)) +
  scale_x_discrete() +
  annotate("rect", 
           xmin = s3_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) - 0.25,
           xmax = s3_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) + 0.25,
           ymin = -Inf,
           ymax = Inf,
           fill = "#dcdcdc") +
  geom_pointrange(position=position_dodge(width=.25)) +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  scale_color_manual(values=c("#0067b1","#c50024")) +
  scale_shape_manual(values=c(17,16)) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.5,.1),
    legend.direction = "horizontal",
    legend.background = element_rect(fill = NA),
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", 
       color="Intervention", shape="Intervention")

@@

s3_diff_plot_bystudy <- s3_scored %>% 
  # spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = recode_factor(condition, 
                              "noInterv" = "Control",
                              .default = "Vaccine Ingredients")) %>% 
  left_join(s3_demo %>% distinct(workerId, study)) %>%
  mutate(study = recode_factor(study, "A" = "Expt. 3A", "B" = "Expt. 3B")) %>%
  group_by(study, condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ungroup() %>%
  left_join(s3_scale_order) %>%
  ggplot(aes(x = reorder(scale,order), y = M, ymin = M-se*2, ymax=M+se*2, 
             color = interaction(condition, study, sep = ": "), 
             shape = interaction(condition, study, sep = ": "))) +
  scale_x_discrete() +
  annotate("rect", 
           xmin = s3_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) - 0.35,
           xmax = s3_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) + 0.35,
           ymin = -Inf,
           ymax = Inf,
           fill = "#dcdcdc") +
  geom_pointrange(aes(group = interaction(condition, study)),
                  position=position_dodge(width=.4), fill = "white") +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  scale_color_manual(values=rep(c("#0067b1","#c50024"), 2)) +
  scale_shape_manual(values=c(17, 16, 24, 21)) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.5,.15),
    legend.direction = "horizontal",
    legend.background = element_rect(fill = NA),
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", 
       color="Intervention", shape="Intervention") +
  guides(shape = guide_legend(nrow = 2, byrow = T),
         color = guide_legend(nrow = 2, byrow = T))

@@

s4_diff_plot <- combined %>% 
  filter(returned==TRUE, !is.na(vacc_news)) %>% # somehow 5? participants slippd by without answering 
  mutate(posttest = rescale_beta(posttest, -3, 3), pretest = rescale_beta(pretest, -3, 3)) %>% 
  mutate(diff = posttest-pretest) %>%
  mutate(
    vacc_news = as.factor(vacc_news),
    scale = recode_nodes2(scale)
    ) %>%
  group_by(vacc_news,scale) %>%
  summarize(
    mean = mean(diff),
    se = sd(diff)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  mutate(vacc_news = factor(vacc_news, 
                            levels = c(0,1), 
                            labels=c("No","Yes"))) %>%
  # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
  left_join(s4_scale_order) %>%
  ggplot(aes(x=reorder(scale, order), 
             y = mean, ymin =ll95, ymax=ul95, 
             color=vacc_news, shape=vacc_news)) +
  scale_x_discrete() +
  annotate("rect", 
           xmin = s4_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) - 0.25,
           xmax = s4_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) + 0.25,
           ymin = -Inf,
           ymax = Inf,
           fill = "#dcdcdc") +
  geom_point(position=position_dodge(width=.25), size=2) +
  geom_errorbar(position=position_dodge(width=.25), width=0) +
  # geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
  geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
  scale_color_manual(values=c("gray50","#C50024")) +
  scale_shape_manual(values=c(17,16)) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.5,.9),
    legend.direction = "horizontal",
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", 
       color="News Exposure", shape="News Exposure")

@@

```{r measles-image, echo=F, fig.align='center', out.height='2in'}
# display measles image here
knitr::include_graphics("img_0.png")
```

@@

```{r mumps-image, echo=F, fig.align='center', out.height='2in'}
# display mumps image here
knitr::include_graphics("img_1.jpg")
```

@@

```{r rubellas-image, echo=F, fig.align='center', out.width='2in'}
# display rubella image here
knitr::include_graphics("img_2.jpg")
```
